The Impact of Past Behavior Normality on Regret: A Replication Study

### 2024-02-15 outputs/paper/Paper_2.qmd
1: organize all files, include delect useless files 2: update read me files, add a LLM introduction

Figure \@ref(fig:fig1) is a replication of Figure 1 in the original paper, In this section, participants evaluated a classic scenario known as the hitchhiker scenario, to assess the impact of past behavior on the perception of regret following negative outcomes. 92% of the 315 participants believed that Mr. Jones, who almost never gives rides to others, felt a stronger sense of regret. The majority of participants believed that Mr. Jones, who almost never picks up hitchhikers, exhibits behavior that is more common in society (95% out of 326 respondents), whereas Mr. Smith, who frequently gives rides to hitchhikers, is more likely to be criticized by society (91% out of 310 respondents). For the assessment of negative affect, 93% of people believed that Mr. Jones experienced more negative affect compared to Mr. Smith. Overall, these two experiments provided very close replications, similar to the the original study.

@@

fig1 <- ggplot(long_data, aes(x = Category, y = Percentage, fill = Group)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  scale_fill_grey(start = 0.8, end = 0.2) + # Adjust the grey scale to match the example
  theme_minimal() +
  labs(
    fill = "", 
    x = "",    
    y = ""     
  ) +
  theme(
    legend.position = "bottom", 
    axis.text.x = element_text(angle = 45, hjust = 1), # Rotate x-axis labels if necessary
    plot.title = element_text(hjust = 0.5) # Center the plot title if you add one
  )
fig1
```

@@

ggplot(data, aes(x = Sc3conditionl1, y = compensationaggrecoded1)) + 
  geom_violin(trim = FALSE) + 
  geom_jitter(shape = 16, position = position_jitter(height = 0.1, width = 0.2)) + 
  theme_apa() +
  labs(x = "Condition", y = "Compensation") +
  scale_y_continuous(minor_breaks = seq(-10, 15, 5)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.9), width = 0.2) +
  stat_summary(fun.y = mean, geom = "point", shape = 18, size = 3)

ggplot(data, aes(x = Sc3conditionl1, y = regretaggrecoded1)) + 
  geom_violin(trim = FALSE) + 
  geom_jitter(shape = 16, position = position_jitter(height = 0.1, width = 0.2)) + 
  theme_apa() +
  labs(x = "Condition", y = "Regret") +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.9), width = 0.2) +
  stat_summary(fun.y = mean, geom = "point", shape = 18, size = 3)

>>>>

Figure1 is a replication of Figure 1 in the original paper, In this section, participants evaluated a classic scenario known as the hitchhiker scenario, to assess the impact of past behavior on the perception of regret following negative outcomes. 92% of the 315 participants believed that Mr. Jones, who almost never gives rides to others, felt a stronger sense of regret. The majority of participants believed that Mr. Jones, who almost never picks up hitchhikers, exhibits behavior that is more common in society (95% out of 326 respondents), whereas Mr. Smith, who frequently gives rides to hitchhikers, is more likely to be criticized by society (91% out of 310 respondents). For the assessment of negative affect, 93% of people believed that Mr. Jones experienced more negative affect compared to Mr. Smith. Overall, these two experiments provided very close replications, similar to the the original study.

@@

fig1 <- ggplot(long_data, aes(x = Category, y = Percentage, fill = Group)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  scale_fill_grey(start = 0.8, end = 0.2) + # Adjust the grey scale to match the example
  theme_minimal() +
  labs(
    fill = "", 
    x = "",    
    y = ""     
  ) +
  theme(
    legend.position = "bottom", 
    axis.text.x = element_text(angle = 45, hjust = 1), # Rotate x-axis labels if necessary
    plot.title = element_text(hjust = 0.5) 
  )
fig1
```

@@

fig3 <- ggplot(data, aes(x = Sc3conditionl1, y = compensationaggrecoded1)) + 
  geom_violin(trim = FALSE) + 
  geom_jitter(shape = 16, position = position_jitter(height = 0.1, width = 0.2)) + 
  theme_apa() +
  labs(x = "Condition", y = "Compensation") +
  scale_y_continuous(minor_breaks = seq(-10, 15, 5)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.9), width = 0.2) +
  stat_summary(fun.y = mean, geom = "point", shape = 18, size = 3)

fig4 <- ggplot(data, aes(x = Sc3conditionl1, y = regretaggrecoded1)) + 
  geom_violin(trim = FALSE) + 
  geom_jitter(shape = 16, position = position_jitter(height = 0.1, width = 0.2)) + 
  theme_apa() +
  labs(x = "Condition", y = "Regret") +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.9), width = 0.2) +
  stat_summary(fun.y = mean, geom = "point", shape = 18, size = 3)

fig3 
fig4
```
